
\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\titleformat{\section}{\scshape\large}{}{0em}{}[\titlerule]

\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\begin{document}

% ---------- HEADING ----------
\begin{center}
  \textbf{\Huge \scshape Saurabh Chauhan} \\ \vspace{3pt}
  \small\href{8544709161}{\raisebox{-0.2\height} \rotatebox[origin=c]{270}\faPhone\ \underline8544709161}
   $|$ \href{mailto:saurabhchauhan1785@gmail.com}{\faEnvelope\underline saurabhchauhan1785@gmail.com}
   $|$ \href{www.linkedin.com/in/saurabh-chauhan-a96413323/}{\raisebox{-0.2\height}\faLinkedin\underline{LinkedIn}}
   $|$ \href{www.github.com/Saurabh-1785}{\raisebox{-0.2\height}\faGithub\underline {GitHub}}
\end{center}

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \textbf{Languages}{: Python, JavaScript, C/C++}
  \item \textbf{Frameworks}{: Flask, TailwindCSS}
  \item \textbf{Libraries}{: React, NumPy, Pandas, Matplotlib}
  \item \textbf{Developer Tools}{: HTML, CSS, Git, GitHub, VS Code}
  \item \textbf{Others}{: PR and Presentation Skills}
\end{itemize}

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Portfolio} \href{www.github.com/Saurabh-1785}{\faLink} $|$ \emph{HTML, CSS, JavaScript}}{}
    \resumeItemListStart
           \resumeItem{A curated collection of my work, projects, and creative endeavors. This space reflects my skills, experience and passion for development.}
         \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Interactive Tip Calculator} \href{www.github.com/Saurabh-1785}{\faLink} $|$ \emph{HTML, CSS, JavaScript}}{}
    \resumeItemListStart
           \resumeItem{Built a simple but effective platform to calculate Tip amount and its distribution among every individual.
Enable users to enter the amount and select the tip percentage and number of people in distribution to calculate tip.}
         \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Truss-Analyzer (Group Project)}  $|$ \emph{Flask, HTML, CSS, JavaScript}}{}
    \resumeItemListStart
           \resumeItem{Allows users to input truss structure data and analyze it using the Direct Stiffness Method.
The application uses Flask as the backend, JavaScript for client-side interactions, and HTML/CSS for the UI.}
         \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Medguard (Group Project)}  $|$ \emph{TensorFlow, Neural Network, Jupyter Notebook, Solidity}}{}
    \resumeItemListStart
           \resumeItem{• Built at Electrothon 7.0, this project provides an general idea for secure and safe management of users medical
data.
• This project demonstrates a basic Hardhat use case. It comes with a sample contract, a test for that contract, and
a Hardhat Ignition module that deploys that contract.}
         \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Developer Student Club}{2025-01-19 -- 2025-08-01}
    {Volunteer}{}
    \resumeItemListStart
           \resumeItem{Active member as a poster editor where we worked with Figma and Canva.
Volunteer at the workshops conducted by GDG.
Volunteer at the workshops conducted by GDG.}
         \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {National Institute of Technology, Hamirpur}{2024 -- 2028}
    {B. Tech CSE - 9.32}{Hamirpur, Himachal Pradesh}


  \resumeSubheading
    {P.N.N.M Geeta Adarsh Vidyalaya}{2022 -- 2023}
    {Class 12 - 95.6\%}{Solan, Himachal Pradesh}

\resumeSubHeadingListEnd

\end{document}
